Case Study (McKenna)

### 2020-05-13 Code/mrp/Case Study (McKenna) .Rmd
Changed the section names.
Adjusting data lists for stan models.

## Data/Categories/Cells
Categorical classification variables are choosen and cell are assigned baised off of category classification. For example, if one variable is gender consisting of two categories (male and other) and one varibale is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.

@@

#### McKenna's logit model  
```{r}
data_list <- list(
  D <- 5,                                                    # Number of variables. 
  N <- 1200,                                                 # Number of observations.
  L <- 6300,                                                 # Number of groups. 
  y <- sample$service_failure,                               # Outcome variables. 
  ll <- sample(6300, 1200, replace = TRUE),                  # Group assignment. 
  x <- matrix(sample %>% 
                select(male, age, eth, income, state))       # Matrix of predictors. 
)

D <- 5
N <- 1200
L <- 6300
y <- sample$service_failure
ll <- sample(6300, 1200, replace = TRUE)

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = "data_list",
  seed = 42
)
```
#### Downes logit model 
```{r}
# Observations. 
outcome <- sample$service_failure
male <- sample$male
age <- sample$age 
eth <- sample$eth 
income <- sample$income
state <- sample$state

# Number of categories. 
n <- length(outcome)
n_male <- max(male)
n_age <- max(age)
n_eth <- max(eth)
n_income <- max(income)
n_state <- max(state)

@@

```{r, eval = FALSE}
stanfit_final <- stan(file= "downes_copy.stan",
                        data=c("n","n_age","n_male","n_eth","n_income","n_state",
                               "outcome","age","male","eth","income","state"), 
                        iter=n_iter, chains=n_chain)
```
#### Stan user guide logit model 
```{r}
stan_data <- list( 
  age <- sample$age, 
  eth <- sample$eth, 
  income <- sample$income, 
  male <- sample$male, 
  state <- sample$state, 
  Y <- sample$service_failure, 
  N <- length(Y))
```

>>>>

## Data 
Categorical classification variables are choosen and cell are assigned baised off of category classification. For example, if one variable is gender consisting of two categories (male and other) and one varibale is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.

@@

#### McKenna's logit model  
```{r}
predictors <- sample %>% 
  select(male, age, eth, income, state)

pred <- as.matrix(predictors, byrow = TRUE)
```

```{r}
data_list <- list(
  D = 5,                                              # Number of variables. 
  N = 1200,                                           # Number of observations.
  L = 6300,                                           # Number of groups. 
  y = sample$service_failure,                         # Outcome variables. 
  ll = sample(6300, 1200, replace = TRUE),            # Group assignment. 
  x = predictors                                      # Matrix of predictors. 
)
```

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = "data_list",
  seed = 42 
)
```
#### Downes logit model 
```{r}
# Observations. 
downes_list <- list(
  outcome = sample$service_failure,
  male = sample$male,
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income,
  state = sample$state,
  n = length(sample$service_failure), 
  n_male = max(sample$male),
  n_age = max(sample$age),
  n_eth = max(sample$eth),
  n_income = max(sample$income),
  n_state = max(sample$state)
)

@@

```{r, eval = FALSE}
stanfit_final <- stan(file = "downes_copy.stan",
                        data = downes_list, 
                        iter = n_iter, chains = n_chain)
```
#### Stan user guide logit model 
```{r}
stan_data <- list( 
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income, 
  male = sample$male, 
  state = sample$state, 
  Y = sample$service_failure, 
  N = length(sample$service_failure))
```
